---
title: "Nonprofit Tweet Analysis Dashboard"
author: "Tiffany Feng"
date: "8/9/2020"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
---

The goal of this project is to derive insights about Twitter trends within the nonprofit industry through the analysis of tweets. This project was created for LA Blueprint, a UCLA student organization that produces technology for Southern California nonprofits.

```{r setup, include=FALSE}
library(dygraphs)
library(flexdashboard)
library(rtweet)
library(ggplot2)
library(dplyr)
library(tidytext)
library(maps)
library(stringr)
library(wordcloud)
library(plotly)
library(DT)
```

```{r, message = FALSE, echo = FALSE}
# Search for 18000 tweets containing "nonprofit"
nonprofit_tweets <- search_tweets(q = "nonprofit",
                              n = 18000)
#load(file = "nptweets.RData")
```

Trends
===================================== 

Row
-------------------------------------
    
### Frequency of tweets containing 'nonprofit'
    
```{r, message = FALSE, echo = FALSE}
p1 <- nonprofit_tweets %>%
  ts_plot("hours", color = "deepskyblue2") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    # title = "Frequency of tweets containing 'nonprofit'",
    # subtitle = "tweet counts aggregated using one-hour intervals",
    subtitle = paste0(format(min(nonprofit_tweets$created_at), "%d %B %Y"), " to ",
                      format(max(nonprofit_tweets$created_at),"%d %B %Y")),
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )

ggplotly(p1)
```
   
    
### Top tweet locations

```{r, message = FALSE, echo = FALSE}
 nonprofit_tweets %>% 
  filter(!is.na(place_full_name)) %>% 
  count(place_full_name, sort = TRUE) %>% 
  # top_n(15) %>% 
  datatable( filter="top", options = list(bPaginate = FALSE), colnames = c("location", "count"))
```

Row
-------------------------------------

### Top 15 hashtags in tweets containing 'nonprofit'

```{r, message = FALSE, echo = FALSE}
top_nonprofit_ht <- nonprofit_tweets %>% 
  unnest_tokens(hashtag, text, "tweets", to_lower = TRUE) %>%
  filter(str_detect(hashtag, "^#"),
        hashtag != "#nonprofit") %>%
  count(hashtag, sort = TRUE) %>%
  top_n(15)

p2 <- ggplot(top_nonprofit_ht, aes(x = reorder(hashtag, n), y = n, fill = n)) +
  geom_bar(stat = "identity") +
    coord_flip() + 
    scale_fill_gradient(low = "salmon", high = "orange") +
    xlab("hashtag") +
    ylab("count") +
    labs(fill = "count")
    #+ ggtitle( "Top 15 hashtags in tweets containing 'nonprofit'")

ggplotly(p2)
```

### Top 15 accounts mentioned in tweets containing 'nonprofit'

```{r, message = FALSE, echo = FALSE}
top_nonprofit_mn <- nonprofit_tweets %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  top_n(15)

p3 <- ggplot(top_nonprofit_mn, aes(x = reorder(mentions, n), y = n, fill = n)) +
  geom_bar(stat = "identity") +
    coord_flip() +
    scale_fill_gradient(low = "blue2", high = "cyan2") +
    xlab("twitter account") +
    ylab("number of mentions") +
    labs(fill = "mentions")
    #+ggtitle("Top 15 mentions in tweets containing 'nonprofit'")

ggplotly(p3)
```

Word Analysis
===================================== 

Column
-------------------------------------
### Tweet Word Frequency Cloud

```{r, message = FALSE, echo = FALSE}
top_nonprofit_words <- nonprofit_tweets %>%
  mutate(text = str_remove_all(text, "&amp;|&lt;|&gt;"),
         text = str_remove_all(text, "\\s?(f|ht)(tp)(s?)(://)([^\\.]*)[\\.|/](\\S*)"),
         text = str_remove_all(text, "[^\x01-\x7F]")) %>% 
  unnest_tokens(word, text, token = "tweets") %>%
  filter(!word %in% stop_words$word,
        !word %in% str_remove_all(stop_words$word, "'"),
        str_detect(word, "[a-z]"),
        !str_detect(word, "^#"),         
        !str_detect(word, "@\\S+")) %>%
  count(word, sort = TRUE)

top_nonprofit_words %>% 
  with(wordcloud(word, n, random.order = FALSE, max.words = 100, colors = "#42bcf5"))
```

Column
-------------------------------------
### Top words used in tweets containing 'nonprofit'

```{r, message = FALSE, echo = FALSE}
top_nonprofit_words %>% 
  top_n(500) %>% 
  datatable(filter="top", options = list(bPaginate = FALSE), colnames = c("word", "count"))
```

