---
title: "Nonprofit Tweet Analysis"
author: "Tiffany Feng"
date: "08/01/2020"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Introduction and Objective           

The goal of this project is to derive insights about Twitter trends within the nonprofit industry through the analysis of tweets. This project was created for LA Blueprint, a UCLA student organization that produces technology for Southern California nonprofits.

```{r, message = FALSE, echo = FALSE}
# installing and loading necessary packages
# install.packages("rtweet")
# install.packages("tidytext")
# install.packages("maps")
# install.packages("wordcloud")
library(rtweet)
library(ggplot2)
library(dplyr)
library(tidytext)
library(maps)
library(stringr)
library(wordcloud)
library(plotly)
library(DT)
```



```{r, message = FALSE, echo = FALSE}
# Search for 18000 tweets containing "nonprofit"
nonprofit_tweets <- search_tweets(q = "nonprofit",
                              n = 18000)
```

# When are tweets being made?

```{r, message = FALSE, echo = FALSE}
p1 <- nonprofit_tweets %>%
  ts_plot("hours", color = "deepskyblue2") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of tweets containing 'nonprofit'",
    # subtitle = "tweet counts aggregated using one-hour intervals",
    subtitle = paste0(format(min(nonprofit_tweets$created_at), "%d %B %Y"), " to ",
                      format(max(nonprofit_tweets$created_at),"%d %B %Y")),
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )

ggplotly(p1)
```

# Where are these tweets coming from?

### Top tweet locations

```{r, message = FALSE, echo = FALSE}
 nonprofit_tweets %>% 
  filter(!is.na(place_full_name)) %>% 
  count(place_full_name, sort = TRUE) %>% 
  # top_n(15) %>% 
  datatable( filter="top", options = list(pageLength = 5), colnames = c("location", "count"))
```

### Current trends in Los Angeles

```{r, message = FALSE, echo = FALSE}
la <- get_trends("los angeles")

la$trend
```


# Top 15 hashtags in tweets containing 'nonprofit'

```{r, message = FALSE, echo = FALSE}
top_nonprofit_ht <- nonprofit_tweets %>% 
  unnest_tokens(hashtag, text, "tweets", to_lower = TRUE) %>%
  filter(str_detect(hashtag, "^#"),
        hashtag != "#nonprofit") %>%
  count(hashtag, sort = TRUE) %>%
  top_n(15)

p2 <- ggplot(top_nonprofit_ht, aes(x = reorder(hashtag, n), y = n, fill = n)) +
  geom_bar(stat = "identity") +
    coord_flip() + 
    scale_fill_gradient(low = "salmon", high = "orange") +
    xlab("hashtag") +
    ylab("count") +
    labs(fill = "count") +
    ggtitle( "Top 15 hashtags in tweets containing 'nonprofit'")

ggplotly(p2)
```

# Top 15 accounts mentioned in tweets containing 'nonprofit'

```{r, message = FALSE, echo = FALSE}
top_nonprofit_mn <- nonprofit_tweets %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  top_n(15)

p3 <- ggplot(top_nonprofit_mn, aes(x = reorder(mentions, n), y = n, fill = n)) +
  geom_bar(stat = "identity") +
    coord_flip() +
    scale_fill_gradient(low = "blue2", high = "cyan2") +
    xlab("twitter account") +
    ylab("number of mentions") +
    labs(fill = "mentions") +
    ggtitle("Top 15 mentions in tweets containing 'nonprofit'")

ggplotly(p3)
```

# Top words used in tweets containing 'nonprofit'

```{r, message = FALSE, echo = FALSE}
top_nonprofit_words <- nonprofit_tweets %>%
  mutate(text = str_remove_all(text, "&amp;|&lt;|&gt;"),
         text = str_remove_all(text, "\\s?(f|ht)(tp)(s?)(://)([^\\.]*)[\\.|/](\\S*)"),
         text = str_remove_all(text, "[^\x01-\x7F]")) %>% 
  unnest_tokens(word, text, token = "tweets") %>%
  filter(!word %in% stop_words$word,
        !word %in% str_remove_all(stop_words$word, "'"),
        str_detect(word, "[a-z]"),
        !str_detect(word, "^#"),         
        !str_detect(word, "@\\S+")) %>%
  count(word, sort = TRUE)

top_nonprofit_words %>% 
  with(wordcloud(word, n, random.order = FALSE, max.words = 100, colors = "#42bcf5"))

top_nonprofit_words %>% 
  top_n(500) %>% 
  datatable(filter="top", options = list(pageLength = 5), colnames = c("word", "count"))
```

